---
title: "Some lab based task"
bibliography: references.bib
biblio-style: apalike
link-citations: yes
params: 
    SHOW_SOLS: TRUE
    TOGGLE: TRUE
---

```{r setup, include=FALSE}
source('assets/setup.R')
```


:::red
**PRE-LAB ACTIVITIES**

Please ensure you have successfully installed R and RStudio, or are working on RStudio Cloud, and that you have completed the tasks on the [ADD URL] page, which introduced the basics of a) how to navigate around Rstudio, b) how to create a Rmarkdown document, c) how to read data into R, and d) how to use R to do basic arithmetic.  
:::

:::lo
**LEARNING OBJECTIVES**

1. Understand...
1. Understand...
1. Understand...

:::


:::green
__Information about solutions__

Solutions for these exercises are available immediately below each question.  
We would like to emphasize that much evidence suggests that testing enhances learning, and we __strongly__ encourage you to make a concerted attempt at answering each question *before* looking at the solutions. Immediately looking at the solutions and then copying the code into your work will lead to poorer learning.  
We would also like to note that there are always many different ways to achieve the same thing in R, and the solutions provided are simply _one_ approach.  
:::



In this lab, we are going to take a look at how to access specific sections of data, before we move on to talking about different types of data.

We encourage you to work along with the reading - open a new RMarkdown document, and run the code which we discuss below.  
   
At the end there is a set of exercises for you to complete. 

# Accessing parts of the data  

Suppose we read some data into R:


```{r}
library(tidyverse)
starwars2 <- read_csv("https://asucbi.github.io/data/starwars2.csv")
```






